\documentclass[12pt]{article}
\setlength{\voffset}{-25mm}
\setlength{\hoffset}{-20mm}
\setlength{\textwidth}{170mm}
\setlength{\textheight}{240mm}
\usepackage{amsmath,amssymb,euscript,amsthm,amsfonts, mathrsfs}

\begin{document}

\begin{center}
\textbf{\Large \sc Title of Abstract}\\[1ex]
\textbf{A.~B. Ivanov$^1$, C.~D. Smith$^2$}\\[0.4ex]
${}^1$Institute of Mathematics of NAS of Ukraine, Kyiv, Ukraine\\
${}^2$Taras Shevchenko National University of Kyiv, Kyiv, Ukraine\\[0.4ex]
\textit{ivanov@domain1.com, smith@domain2.com} %e-mail
\end{center}


Please use this template to prepare your abstract.
Please note that it should not exceed one page.
The file should be renamed using family names of first two coauthors as in the following example: \texttt{ivanov-smith.tex}.


Both TeX and PDF files of your abstract should be sent
 to {\bf iacu2017@gmail.com}\,.
The deadline for submission of abstracts is {\bf May 15, 2017}.




Please do not use automatical numbering of formulas and references. The following format should be used
$$
 x'=Ax.  \eqno{(1)}
$$


Reference to equation (1). Reference to article or book [2].





\textbf{Theorem.} \textit{Statement of the theorem.}


\vskip 2 mm

{\small\it Put you acknowledgements at the end of main text but before references in such style. }


{\small
\begin{enumerate}
\setlength{\itemsep}{-0.5mm}

\item Author A.~B. Title of article. Journal name, Year, Volume, Pages.
\item Author C.~D. Title of book.~-- City: Publisher, Year, Number of pages.

\end{enumerate}
}

\end{document}
